### 2023-01-27 article.tex
Add Barba

This paper defines paradata as 'data about the data collection 
process' \cite{choumert2019using}.
This definition is chosen for its simplicity, 
yet there are multiple related and/or more nuanced 
definitions of paradata (see \cite{huvila2022improving} for an overview).

@@

Nowadays, the lack of paradata can be seen as 'a drastic constraint'
in data use \cite{huvila2022improving}.
Computer code, being paradata, the effect of its absence is, most obviously,
that a computational experiment cannot be redone easily.
yet there are wider implications as well.

@@

A scientific claim must be reproducible before it is accepted
by the scientific community.
Reproducibility (i.e. to reproduce the same results) 
and replicability (i.e. to reconclude a conclusion)
are fundamental characteristics of scientific studies \cite{patil2019visual}.
For computational science, theoretically, it should be relatively easy to 
reproduce an experiment, as all it takes is a computer, electricity,
an optional internet connection, the code and the data.
In practice, however, it appears that 
the academic culture to reproduce results 
has been lost over time \cite{peng2011reproducible}.
That same study recommended, as a solution to counter this, 
to make reproducible research a minimal requirement for 
publication \cite{peng2011reproducible}.

>>>>

This paper defines paradata as 'data about the data collection 
process' \cite{choumert2019using}.
This definition is chosen for its simplicity, 
yet there are multiple related and/or more nuanced 
definitions of paradata (see for example \cite{huvila2022improving} 
and \cite{skold2022interrogating}).

@@

Nowadays, the lack of paradata can be seen as 'a drastic constraint'
in data use \cite{huvila2022improving}.
Computer code, being paradata, the effect of its absence is, most obviously,
that a computational experiment cannot be redone 
easily,
yet there are wider implications as well.

@@

A scientific claim must be reproducible before it is accepted
by the scientific community.
Reproducibility (i.e. to reproduce the same results) 
and replicability (i.e. to reconclude a conclusion)
are fundamental characteristics of scientific studies \cite{patil2019visual}.
For computational science, theoretically, it should be relatively easy to 
reproduce an experiment, as all it takes is a computer, electricity,
an optional internet connection, the code and the data.
In practice, however, it appears that 
the academic culture to reproduce results 
has been lost over time in general \cite{peng2011reproducible},
with labs that embrace reproducibility (for example, \cite{barba2016hard})
are the exception.

That same study recommended, as a solution to counter this, 
to make reproducible research a minimal requirement for 
publication \cite{peng2011reproducible}.
